\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-09-28 paper/manuscript_jitp_rr2.tex
removed fragment

\hl{Though our main focus in the current article is on the application to government websites, it is important to note that the pipeline we develop will be useful in the context of many other research designs that involve the collection of website content. Though we are not familiar with existing applications of automated text analysis to government websites, previous work in other domains has involved computational content analysis of websites.} \hl{For example, }\citet{coyle2020no} \hl{analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.} \citet{kluver2015measuring} \hl{use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.}

>>>>

\hl{Though our main focus in the current article is on the application to government websites, it is important to note that the pipeline we develop will be useful in the context of many other research designs that involve the collection of website content. Previous work in other domains has involved computational content analysis of websites.} \hl{For example, }\citet{coyle2020no} \hl{analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.} \citet{kluver2015measuring} \hl{use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.}
